---
title: "Datasaurus, one file"
output: 
  html_document:
    theme: cosmo
date: "7th February 2023"
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(targets)
# We specify we will use the project ds_linear which 
# correspond to the target file: _targets_ds_1.R and store `_ds_1/` (config: `_targets.yaml`)
Sys.setenv(TAR_PROJECT = "ds_linear")
```

## Literate programming using targets

Read more in [William Landau](https://wlandau.github.io/about.html) `targets` [manual](https://books.ropensci.org/targets/literate-programming.html).

Dependencies of this Rmakrdown document are based on the parsing of the `tar_read()` and `tar_load()` calls within it.

### Tibble

- `tar_load()` read the target (by default a `rds` saved object) and load it in the GlobalEnv with the target name.
- `tar_read()` only reads the targets and returns it. No assignment is made.

```{r}
tar_load(ds)
ds
```

### Compute summary statistics


```{r}
ds |> 
  group_by(dataset) |>
  summarise(across(c(x, y), list(mean = mean, sd = sd)))
```



### Facet plot

```{r}
#| fig-height: 10
#| fig-width: 8
tar_read(all_facets)
```

### Animation

```{r}
#| echo: false
knitr::include_graphics(tar_read(gif))
```


### Directed Acyclic Graph

Show dependencies, optionally with the time it took to build and disk space used.

```{r}
tar_visnetwork(label = c("time", "size"))
```


