---
title: "Datasaurus, dynamic branching"
output: 
  html_document:
    theme: cosmo
date: "7th February 2023"
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(targets)
# We specify we will use the project ds_dynamic which 
# correspond to the target file: _targets_ds_2.R and store `_ds_2/` (config: `_targets.yaml`)
Sys.setenv(TAR_PROJECT = "ds_dynamic")
```


### Input files

13 tabulated-separated-values to read from one folder `data`:

```{r}
tar_read(dset) |> 
  enframe()
```

Dynamic branches create hash names, we will explore [static branching](https://books.ropensci.org/targets/static.html) to get meaningful branch names.


### Tibble


After the 13 files were read with [dynamic branching](https://books.ropensci.org/targets/dynamic.html), the _magic_ aggregation (like `bind_rows()`) is done by simply calling the target **name**.

This is done by `iteration = "vector"` in `tar_target()` b(the default value).

```{r}
tar_read(ds)
```


Individual tibble can be retrieved by `branches`

```{r}
# Only the 'star' dataset 
tar_read(ds, branches = 2L)
```


### Plots

Individual plot, `tar_read()` but iteration had to be `list` since `ggplot` object cannot be bundled as tibbles or atomic elements. 

```{r}
tar_read(plots, branches = 2L)
```


Then you can use the **list** `plots` to make one figure with [`patchwork`](https://patchwork.data-imaginist.com/)

- Recursively change the `theme` of all plot
- Add a main title

```{r}
#| fig-height: 10
#| fig-width: 11
library(patchwork)
wrap_plots(tar_read(plots)) +
   plot_annotation(title = "13 datasets bundled with patchwork") & theme_void()
```



### Directed Acyclic Graph

Show dependencies, optionally with the time it took to build and number of branches.

It all appears as outdated since `tar_files()` is agnostic to the files to explore, meaning this target is executed each time.
For comparison, you can use `tar_files_input()` when files are **already** present as explained [in the docs](https://docs.ropensci.org/tarchetypes/reference/tar_files_input.html#details).

```{r}
tar_visnetwork(label = c("time", "branches"))
```


